---
title: "capitalize"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{capitalize}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidybibtex)
```

## Load a BibTeX file 

The package contains a sample BibTeX file called `sample_bib.` Note that this object is a character vector. If you want to import your own BibTeX file, please use the `readLines()` function. It's a base R function, so you don't need to install any new library.

```{r}
sample_bib[1:10]
```

## Capitalize a selected field 

In case you want to capitalize the title field. 

```{r}
capitalize_field(vec = sample_bib[1:10], 
                 field = "title")
```

In case you want to capitalize the title field except "in" and "the."

```{r}
capitalize_field(vec = sample_bib[1:10], 
                 field = "title",
                 exceptions = c("in", "the"))
```

## Load and capitalize by one function

You can simply the above steps using the `cap_bib_field()` function.

```{r eval = FALSE}
cap_bib_field(file_path = <Insert the file path>,
              vec = sample_bib[1:10], 
              field = "title",
              exceptions = c("in", "the"))
```

## If you want to export the modified BibTeX file 

```{r eval = FALSE}
# writeLines is a base R function.
writeLines(<object name>, <file path>)
```
